Hydra Battles and Cie

### 2021-06-28 doc/hydras.tex

\author{Pierre Castéran\\ LaBRI, Univ. Bordeaux, CNRS UMR 5800, \thanks{With contributions by Yves Bertot, \'Evelyne Contejean,  Florian Hatat and Pascal Manoury. The formalization of primitive recursive functions was originally authored by 
Russel O'Connor\cite{OConnor05}.}}
\date{\today}
\title{Hydra Battles and Cie}
\makeindex{coq}
\makeindex{maths}
\makeindex{hydras}
\makeindex{additions}
\makeindex{primrec}
\begin{document}
\maketitle

@@

\section{Acknowledgements}
\label{sec:orgheadline5}
    Many thanks to Yves Bertot, \'Evelyne Contejean,  Florian Hatat,  David Ilcinkas, 
Pascal Manoury,  Karl Palmskog, Sylvain Salvati, Alan Schmitt and Théo Zimmerman for their help on the elaboration of this document, and to the
 members of the \emph{Formal Methods} team and the \emph{Coq working group} at laBRI for their helpful comments 
on  oral presentations of this work.

>>>>

\author{Pierre Castéran\\ LaBRI, Univ. Bordeaux, CNRS UMR 5800, \thanks{With contributions by Yves Bertot, \'Evelyne Contejean,  Jérémy Damour, Florian Hatat, Pascal Manoury and Théo Zimmermann. The formalization of primitive recursive functions was originally authored by 
Russel O'Connor\cite{OConnor05}.}}
\date{\today}
\title{Hydra Battles and Cie}
\makeindex{coq}
\makeindex{maths}
\makeindex{hydras}
\makeindex{additions}
\makeindex{primrec}
\begin{document}
\maketitle

@@

\section{Acknowledgements}
\label{sec:orgheadline5}
    Many thanks to Yves Bertot, \'Evelyne Contejean,  Florian Hatat,  David Ilcinkas, 
Pascal Manoury,  Karl Palmskog, Sylvain Salvati, Alan Schmitt and Théo Zimmermann for their help on the elaboration of this document, and to the
 members of the \emph{Formal Methods} team and the \emph{Coq working group} at laBRI for their helpful comments 
on  oral presentations of this work.
